---
title: "p8105_hw3_tw2838"
author: "Tianyou Wang"
date: "2022-10-15"
output: html_document
---

## Setting Opotions

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(p8105.datasets)
library(ggridges)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



# Problem #1 Instacart

```{r}
data("instacart")
```

Instacart is an online grocery service that allows you to shop online from local stores. The original dataset contains 1,384,617 observations (rows) of 131,209 unique users, where each row in this dataset is a product from an order. Additionally, each row is characterized by `r ncol(instacart)` variables, including user_id, ordering time, aisle and department information etc. In total, we followed `r n_distinct(instacart$order_id)` orders which are placed across `r min(instacart$order_hour_of_day)`AM to `r max(instacart$order_hour_of_day)`PM throughout the week. Number of days since the last order is tracked through the "days_since_prior_order" variables which is capped at 30. Finally, this dataset involves `r n_distinct(instacart$product_name)` different kinds of products from `r n_distinct(instacart$department)` departments.



### *How many aisles, and which aisles are the most items ordered from?*

```{r}
n_aisle = 
  instacart %>% 
  group_by(aisle) %>% 
  summarise(n_order = n())

nrow(n_aisle)

aisle_most = 
  n_aisle %>% 
  filter(min_rank(desc(n_order)) == 1)
```

In this dataset, we have `r nrow(n_aisle)` different aisles, and the aisle "`r aisle_most$aisle`" have the most ordered items. There are `r aisle_most$n_order` orders.



### *Make a plot that shows the number of items ordered in each aisle*
Note: We are limiting this to aisles with more than 10000 items ordered/

```{r fig.width = 16, fig.asp=0.5}
n_aisle %>%
  filter(n_order > 10000) %>% 
  ggplot(aes(x=n_order/1000, y=aisle, fill=aisle)) +
  geom_bar(stat = "identity", alpha = 0.75) +
  labs(title = "Number of Items Ordered in Each Aisle",
       x = "Number of Item Ordered (in thousands)",
       y = "Aisles") +
  scale_x_continuous(
    breaks = c(0, 15, 50, 75, 100, 125, 150)) +
  theme(legend.position = "None")
```



### *Make a table showing the three most popular items in some aisles*
I am making table to show the three most popular items in “baking ingredients”, “dog food care”, and “packaged vegetables fruits” aisles. Including the number of times each item is ordered.

```{r message=FALSE, warning=FALSE}
aisle_df =
  instacart %>% 
  filter(aisle == c("baking ingredients", 
                    "dog food care", 
                    "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarise(n_order = n()) %>% 
  filter(min_rank(desc(n_order)) < 4)
```

```{r}
knitr::kable(aisle_df)
```



### *Mean ordered time for some product across the week*
Making a table to show the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week. Formatting this table as a 2 x 7 table.

```{r message=FALSE, warning=FALSE}
mean_df =
  instacart %>% 
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hr = round(mean(order_hour_of_day, na.rm = TRUE),1)) %>%
              pivot_wider(
                names_from = order_dow, 
                values_from = mean_hr)

knitr::kable(mean_df)              
```





# Problem #2 Accelerometer, Activity Counts

### *Load, tidy, and understand the data*

```{r message=FALSE, warning=FALSE}
accel_df = 
  read_csv(
    "data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(day_code = recode(day, "Monday" = "weekday", 
                           "Tuesday" = "weekday", 
                           "Wednesday" = "weekday",
                           "Thursday" = "weekday", 
                           "Friday" = "weekday", 
                           "Saturday" = "weekend", 
                           "Sunday" = "weekend")) %>%
  pivot_longer(activity_1:activity_1440, 
               names_to = "measure", 
               names_prefix = "activity_", 
               values_to = "value")
```

I change the format of the data set through `pivot_longer`. Two new variables are created. "measure" stores the accelerometer measurement times, and "value" saves the measured activity count values. We also have 4 more variable, including "week", "day_id", "day", and "day_code." There are total `r nrow(accel_df)` observations. We have `r n_distinct(accel_df$measure)` distinct measurements everyday for `r n_distinct(accel_df$week)` weeks.



### *total activity over the day*

```{r message=FALSE, warning=FALSE}
total_df =
  accel_df %>% 
  mutate(code = recode(day, "Monday" = "1_Mon", 
                           "Tuesday" = "2_Tue", 
                           "Wednesday" = "3_Wed",
                           "Thursday" = "4_Thur", 
                           "Friday" = "5_Fri", 
                           "Saturday" = "6_Sat", 
                           "Sunday" = "7_Sun")) %>%
  group_by(week, code) %>% 
  summarise(total_activity = round(sum(value, na.rm = TRUE), 0))

total_df_wider =
  total_df %>% 
  pivot_wider(names_from = code, 
              values_from = total_activity)
```

```{r}
knitr::kable(total_df_wider)
```

```{r}
ggplot(total_df, aes(x = code, y = total_activity, group = week, color = week)) +
  geom_point() +
  geom_line() +
  labs(title = "Daily Total Activity Across the Week",
       x = "Day",
       y = "Total Activity") +
  theme(legend.position = "bottom")
```

According to the scatter plot, there is no clear total daily activity trend. The change among daily total activity is relatively stable from Tuesday to Thursday in these 5 weeks.



### *plot that shows the 24-hr activity time*

```{r eval=FALSE}
ggplot(accel_df, aes(x = measure, y = value, group = day_id, color = week)) +
  geom_density_ridges() +
  labs(title = "24-hr Activity Track",
       x = "Time",
       y = "Measured Activity") +
  theme(legend.position = "bottom")
```

```{r fig.width = 16, fig.asp=0.4}
accel_df %>% 
  mutate(measure = as.integer(measure)) %>% 
ggplot(aes(x = measure, y = value, group = day_id, color = week)) +
  geom_point(alpha = 0.3) +
  labs(title = "24-hr Activity Track",
       x = "Time",
       y = "Measured Activity") +
    scale_x_continuous(breaks = c(0, 1440), 
                     labels = c("12:00am", "11:59pm")) +
  theme(legend.position = "bottom")
```








# Problem #3 NY NOAA Data

```{r}
data("ny_noaa")
```


